\documentclass[12pt]{article} 
\usepackage{calc}
\usepackage[margin={1in,1in}]{geometry} 
\usepackage[hwkhandout]{hwk}
\usepackage[pdftitle={Calc 1
  Notes},colorlinks=true,urlcolor=blue]{hyperref}
%\usepackage{mathpazo}
\usepackage{multicol}

\renewcommand{\theclass}{\textsc{math}1300: calculus I}
\renewcommand{\theauthor}{Tyson Gern}
\renewcommand{\theassignment}{Differential Equations}
\renewcommand{\dateinfo}{section 6.3}

\newcommand{\ds}{\displaystyle}

\begin{document}
\drawtitle

\begin{enumerate}

\item Find the solution to the initial value problem.
  \begin{align*}
    \frac{dy}{dx}=6x^2+4x, &&& y(2)=10.
  \end{align*}

  \vfill

\item Find the solution to the initial value problem.
  \begin{align*}
    \frac{dP}{dt}=10e^t, &&& P(0)=25.
  \end{align*}

  \vfill

  \newpage

\item A revenue, $R(p)$ is obtained by a farmer from selling grain at
  a price $p$ dollars/unit. The marginal revenue is given by
  $R'(p)=25-2p$.
  \begin{enumerate}
  \item Find $R(p)$. Assume the revenue is zero when the price is
    zero.

    \vfill
    
  \item For what prices does the revenue increase as the price
    increases? For what prices does the revenue decrease as the price
    increases?

    \vfill
    
  \end{enumerate}

  \newpage

\item A car goes from 0 to 80 mph in six seconds with constant
  acceleration, what is the acceleration?

  \vfill

\item A 727 jet needs to attain a speed of 200 mph to take off. If it
  can accelerate from 0 to 200 mph in 30 seconds, how long must the
  runway be? (Assume constant acceleration)

  \vfill

  \newpage

\item Ice is forming on a pond at a rate given by
  \[
  \frac{dy}{dt}=k\sqrt{t},
  \]
  where $y$ is the thickness of the ice in inches at time $t$ measured
  in hours since the ice started forming, and $k$ is a positive
  constant.  Find $y$ as a function of $t$.

  \vfill

\item Show that $y=xe^{-x}+2$ is a solution of the initial value problem
  \begin{align*}
  \frac{dy}{dx} = (1-x)e^{-x},&&& y(0)=2.
  \end{align*}

  \vfill

  \newpage

\item A tomato is thrown upward from a bridge 25m above the ground at
  40m/sec.
  \begin{enumerate}
  \item Give formulas for the acceleration, velocity, and height of
    the tomato at time $t$.

    \vfill
    
  \item How high does the tomato go, and when does it reach its
    highest point?

    \vfill
    
  \item How long is it in the air?

    \vfill
    
  \end{enumerate}

\end{enumerate}

\end{document}
