\documentclass[11pt]{article} 
\usepackage{calc}
\usepackage[margin={1in,1in}]{geometry} 
\usepackage[hwkhandout]{hwk}
\usepackage[pdftitle={Calc 1
  Information},colorlinks=true,urlcolor=blue]{hyperref}


\renewcommand{\theclass}{\textsc{math} 1300-013: Calculus I}
\renewcommand{\theauthor}{Tyson Gern}
\renewcommand{\theassignment}{Introduction}
\renewcommand{\dateinfo}{Fall 2012}

\def\ww{WeBWorK }

\begin{document}
\drawtitle

\section*{General Information}
\begin{description}
\item[Instructor] Tyson Gern
  (\href{mailto:tyson.gern@colorado.edu}{tyson.gern@colorado.edu})
\item[Teaching Assistant] Andrew Healy
\item[Class] Class will be held 12:00--12:50\textsc{pm} every weekday
  in MUEN D144.  You will have lecture with Tyson every day except
  Thursday, when you will have tutorial with Andrew.  The course will
  move rather quickly, so it is vital that you come to every class.
\item[Office Hours] I will hold office hours from
  11:00--11:50\textsc{am} on Monday and Wednesday in my office, Math
  364.  I urge all of you to come to office hours often in order to
  get help on homework and difficult concepts.  The UMRC (help lab) is
  also a great place to get homework help.  It is open 9--5 MTWR and
  9--2 F in Math 175, and is staffed by graduate student instructors,
  many of whom teach Calc I.  I work in the help lab on Tuesday,
  9:00--11:00\textsc{am}.
\item[Course Webpages] I will maintain a webpage with information
  specific to our section at
  \begin{center}
    \url{http://www.tysongern.com/1300f12}.
  \end{center}
  The main course webpage contains general course information at
  \begin{center}
      \url{http://math.colorado.edu/math1300}.
  \end{center}
  Please check these websites daily for information relevant to the
  course.
\end{description}

\section*{Course Information}
\begin{description}
\item[Syllabus] The course syllabus contains information regarding
  exams, homework, and other class requirements.  You can find a copy
  of the syllabus at the following address:
  \begin{center}
    \url{http://math.colorado.edu/math1300/math1300syll.pdf}.
  \end{center}
  Please make sure that you read the entire syllabus and make sure to
  come to me with an questions.

\item[Webwork] As mentioned on the syllabus there will be daily online
  homework.  Please visit
  \begin{center}
    \url{http://webwork.colorado.edu/signup}
  \end{center}
  in order to create an account.  You \textbf{must} enter the correct
  section number (002) and enter your student ID number in order to
  get credit for the online homework.  The first assignment will be
  given on Tuesday, January 17.

\item[Written Homework] In accordance with the syllabus you will also
  have weekly written homework due each Friday.  You can find homework
  standards and grading information on our section's resources page:
  \begin{center}
    \url{http://www.tysongern.com/1300f12/resources}
  \end{center}
  Please make sure you follow the homework standards carefully.
  Failure to do so may result in loss of credit for an assignment.
\end{description}

\section*{Disability Services}
\begin{description}
  \item If you qualify for accommodations because of a disability, please
  submit to me a letter from Disability Services in a timely manner so
  that your needs be addressed. Disability Services determines
  accommodations based on documented disabilities. Contact:
  303-492-8671, Center for Community N200, and
  \begin{center}
  \url{http://www.colorado.edu/disabilityservices}.
  \end{center}

\item If you have a temporary medical condition or injury, see
  guidelines at
  \begin{center}
    \url{http://www.colorado.edu/disabilityservices/go.cgi?select=temporary.html}.
  \end{center}

\item Disability Services' letters for students with disabilities
  indicate legally mandated reasonable accommodations. The syllabus
  statements and answers to Frequently Asked Questions can be found at
  \begin{center}
    \url{http://www.colorado.edu/disabilityservices}.
  \end{center}
\end{description}

\end{document}
