\documentclass[11pt]{article} 
\usepackage{calc}
\usepackage[margin={1in,1in}]{geometry} 
\usepackage[hwkhandout]{hwk}
\usepackage[pdftitle={Calc 1
  Notes},colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{graphicx, tikz}

\renewcommand{\theclass}{\textsc{math}1300: calculus I}
\renewcommand{\theauthor}{Tyson Gern}
\renewcommand{\theassignment}{Chapter 3 \& 4 Worksheet}
\renewcommand{\dateinfo}{review}

\newcommand{\ds}{\displaystyle}

\begin{document}
\drawtitle

\noindent Please answer the following questions completely, showing all work.
If you use your calculator please indicate how it was used.  Clearly
state each answer.

\begin{enumerate}
\item Find the tangent line approximation for $\sqrt{2 + x}$ near
  $x=0$.

  \vfill
  {\color{blue}
  If $f(x)=\sqrt{2+x}$ then $f'(x)=\frac{1}{2}\cdot(2+x)^{-1/2}$, so
  the tangent line $\ell(x)$ is given by
  \begin{align*}
    \ell(x) &= f(0) + f'(0)(x - 0) \\
    &= \sqrt(2) + \frac{1}{2\sqrt{2}}x.
  \end{align*}
  }
  \vfill

\item A voltage $V$ across a resistance $R$ generates a current
  $I=\frac{V}{R}$.  If a constant voltage of 6 volts is put across a
  resistance that is increasing at a rate of $0.7$ ohms per second
  when the resistance is 3 ohms, at what rate is the current
  changing?  Include units in your answer.

  \vfill
  {\color{blue}
  Since the voltage is always constant we have
  \[
  I=\frac{6}{R}=6\cdot R^{-1}.
  \]
  We want to find $\frac{dI}{dt}$, so if we take the derivative with
  respect to $t$ we have
  \[
  \frac{dI}{dt}=6\cdot(-1)R^{-2}\cdot\frac{dR}{dt},
  \]
  so when $R=3$
  \[
  \frac{dI}{dt} = 6\cdot (-1)3^{-2}\cdot (.7) = -\frac{7}{15}.
  \]
  }
  \vfill
  \newpage
  
\item A rectangle has one side on the $x$-axis and two vertices on the
  curve $y=\frac{1}{1 + x^2}$. Find the vertices of the rectangle with
  maximum area.

  \vfill
  {\color{blue}  
  Using the following picture
  \begin{center}
    \begin{tikzpicture}[scale=2.5]
      \def\xmin{-2}
      \def\xmax{2}
      \def\ymin{0}
      \def\ymax{1.2}
      
      \draw[color=red, very thick] (-1,0) -- (-1,.5) -- (1,.5) -- (1,0) -- (-1,0);
      
      \node at ( .5, .1) {$x$};
      \node at ( 1.1, .2) {$y$};
      
      \draw[->] (\xmin,0) -- (\xmax,0);
      \draw[->] (0,\ymin) -- (0,\ymax);
      
      \draw[color=blue, thick, domain=\xmin:\xmax] plot[id=x,samples=100]
      function{1/(1+x*x)};
    \end{tikzpicture}
  \end{center}
  we can see that the area of the rectangle is given by $A=2xy$.  Then
  we know that $y=\frac{1}{1+x^2}$, so
  \[
  A=\frac{2x}{1+x^2}.
  \]
  We know that $x$ is a length, so it must be positive.  Then we only
  need to consider $x$-values in the interval $[0,\infty)$.  To
  maximize the area we will find the critical points, and compare the
  area of the rectangle at the critical points to the area at the
  endpoints.

  Taking derivatives we see that
  \[
  \frac{dA}{dx} = \frac{2+2x^2-4x^2}{(1+x^2)^2} =
  \frac{2-2x^2}{(1+x^2)^2}.
  \]
  The denominator of the derivative is never zero, so to find the
  critical points we need to find where the numerator is zero.  This
  happens when $x=\pm 1$.  Since we are only considering positive
  values of $x$, the only critical point is at $x=1$.  Then
  \begin{align*}
    A(0) &= 0\\
    A(1) &= 1\\
    \lim_{x\to\infty} A(x) &= 0,
  \end{align*}
  so we have a global maximum area of 1 when $x=1$.  Then the vertices
  of the rectangle with maximum area are $(1,0)$, $(1,.5)$, $(-1.0)$,
  and $(-1,-5)$.
  }
  \vfill
  
  \newpage
  
\item Two particles move in the $xy$-plane.  At time $t$, the position
  of particle $A$ is given by $x(t) = 5t - 5$ and $y(t) = 2t - k$, and
  the position of particle $B$ is given by $x(t) = 4t$ and $y(t) = t^2
  - 2t - 1$.
  \begin{enumerate}
  \item If $k=-7$ do the particles ever collide?

    \vfill
    {\color{blue}
    We see that the $x$-coordinates are equal when
    \begin{align*}
      5t-5 &= 4t\\
      t-5 &= 0\\
      t &= 5.
    \end{align*}
    At $t=5$ the $y$-coordinate of particle $A$ is $y(5)=2\cdot 5 -
    (-7)= 17$ and the $y$-coordinate of particle $B$ is
    $y(5)=5^2-2\cdot 5 -1 = 14$, so the particles do not collide,
    since they are never in the same place at the same time.
    }
    \vfill
    
  \item Find $k$ so that the two particles are certain to collide.

    \vfill
    {\color{blue}
    From the discussion above we see that the $x$-coordinates of the
    two particles are the same when $t=5$.  If the particles are to
    collide, we need the $y$-coordinates to be equal at $t=5$, so
    \begin{align*}
      2\cdot 5 -k &= 5^2-2\cdot 5 -1\\
      10-k &= 14\\
      k &= -4
    \end{align*}
    }
    \vfill
    
  \item At the time the particles collide in part (b), which is moving
    faster?

    \vfill
    {\color{blue}
    The speed of particle $A$ is given by
    \[
    \text{speed} = \sqrt{(5)^2+(2)^2}=\sqrt{29}\approx 5.38516.
    \]
    The speed of particle $B$ is given by
    \[
    \text{speed} = \sqrt{(4^2)+(2t-2)^2} = \sqrt{16+64} \approx 8.94427,
    \]
    So particle $B$ is moving faster when they collide.
    }
    \vfill
  \end{enumerate}
  \newpage

\item In parts (a) and (b) determine whether the limit exists, and
  where possible evaluate it.
  \begin{enumerate}
  \item $\displaystyle\lim_{x\to \pi}\frac{\sin^2(x)}{x-\pi}$

    \vfill
    {\color{blue}
    If we try to plug in $x=\pi$ to the above equation we get
    $\frac{0}{0}$, so we can use l'Hopital's rule to solve the limit.
    Taking derivatives we obtain
    \begin{align*}
      \displaystyle\lim_{x\to \pi}\frac{\sin^2(x)}{x-\pi} &= \displaystyle\lim_{x\to \pi}\frac{2\sin(x)\cos(x)}{1}\\
      &= \frac{2\cos(\pi)\sin(\pi)}{1}\\
      &= 0.
    \end{align*}
    }
    \vfill
    
  \item $\displaystyle\lim_{n\to \infty}\sqrt[n]{n}$

    \vfill
    {\color{blue}
    We rewrite the above limit as $\displaystyle\lim_{n\to
      \infty}n^{\frac{1}{n}}$. If we try to plug in $n=\infty$ we get
    $\infty^0$, an indeterminate form.  We now need to get the limit
    in the correct form to use l'Hopital's rule.  Let
    \[
    L = \displaystyle\lim_{n\to \infty}n^{\frac{1}{n}}
    \]
    Then
    \begin{align*}
      \ln(L) &= \lim_{n\to \infty}\ln\left(n^{\frac{1}{n}}\right)\\
      &= \lim_{n\to \infty}\frac{1}{n}\ln(n)\\
      &= \lim_{n\to \infty}\frac{\ln(n)}{n}.
    \end{align*}
    If we plug in $n=\infty$ to the above limit we get
    $\frac{\infty}{\infty}$, so we can use l'Hopital's rule.  Then
    \begin{align*}
      \ln(L) &= \lim_{n\to \infty} \frac{\frac{1}{n}}{1}\\
      &= \lim_{n\to\infty}\frac{1}{n}\\
      &= 0,
    \end{align*}
    so $L=e^0=1$.
    }
    \vfill
  \end{enumerate}
  \newpage


\item Let $f(x)=x-\ln(x)$ for $0.1\leq x\leq 2$. Find the value(s) of
  $x$ for which:
  \begin{enumerate}
  \item $f(x)$ has a critical point. Indicate which ones are maxima
    and which are minima.

    \vfill
    {\color{blue}    
      We see that $f'(x) = 1-\frac{1}{x}$.  Then $f'(x)$ does not exist
      when $x=0$ and is zero when $x=1$.  Since $x=0$ is not in the
      above interval, the only critical point of $f$ occurs at $x=1$.
      We see that $f'(.5)=-1$ and $f'(2)=.5$, so $f$ has a local minimum
      at $x=1$ by the first derivative test.
    }
    \vfill
    
  \item $f(x)$ has a global maximum or global minimum.

    \vfill
    
    {\color{blue}
    Since $f$ continuous on $[.1,2]$ we know that $f$ has both a
    global max and a global min on the interval.  We see that
    \begin{align*}
      f(.1) &\approx 2.40259\\
      f(1) &= 0\\
      f(2) &= 1.30685,
    \end{align*}
    so $f$ has a global max of 2.40259 at $x=.1$ and a global min of 0
    at $x=1$.
    }
    \vfill
  \end{enumerate}
  \newpage
  
\item State the Mean Value Theorem.

  \vfill

  {\color{blue}

    If $f$ is continuous on $a\leq x\leq b$ and differentiable on $a<
    x < b$, then there exists a number $c$, with $a< c < b$, such that
    \[
    f'(c) = \frac{f(b)-f(a)}{b-a}.
    \]
    
  }

  \vfill

\end{enumerate}

\end{document}
