\documentclass[11pt]{article} 
\usepackage{calc}
\usepackage[margin={1in,1in}]{geometry} 
\usepackage[hwkhandout]{hwk}
\usepackage[pdftitle={Calc 1
  Notes},colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{graphicx, tikz}

\renewcommand{\theclass}{\textsc{math}1300: calculus I}
\renewcommand{\theauthor}{Tyson Gern}
\renewcommand{\theassignment}{Chapter 3 \& 4 Worksheet}
\renewcommand{\dateinfo}{review}

\newcommand{\ds}{\displaystyle}

\begin{document}
\drawtitle

\noindent Please answer the following questions completely, showing
all work.  Clearly state each answer.

\begin{enumerate}
\item Find the tangent line approximation for $\sqrt{2 + x}$ near
  $x=0$.

  \vfill

\item A voltage $V$ across a resistance $R$ generates a current
  $I=\frac{V}{R}$.  If a constant voltage of 6 volts is put across a
  resistance that is increasing at a rate of $0.7$ ohms per second
  when the resistance is 3 ohms, at what rate is the current
  changing?  Include units in your answer.

  \vfill
  \newpage
  
\item A rectangle has one side on the $x$-axis and two vertices on the
  curve $y=\frac{1}{1 + x^2}$. Find the vertices of the rectangle with
  maximum area.

  \newpage

\item Two particles move in the $xy$-plane.  At time $t$, the position
  of particle $A$ is given by $x(t) = 5t - 5$ and $y(t) = 2t - k$, and
  the position of particle $B$ is given by $x(t) = 4t$ and $y(t) = t^2
  - 2t - 1$.
  \begin{enumerate}
  \item If $k=-7$ do the particles ever collide?
    

    \vfill
    
  \item Find $k$ so that the two particles are certain to collide.

    \vfill
    
  \item At the time the particles collide in part (b), which is moving
    faster?

    \vfill
  \end{enumerate}
  \newpage

\item In parts (a) and (b) determine whether the limit exists, and
  where possible evaluate it.
  \begin{enumerate}
  \item $\displaystyle\lim_{x\to \pi}\frac{\sin^2(x)}{x-\pi}$

    \vfill
    
  \item $\displaystyle\lim_{n\to \infty}\sqrt[n]{n}$

    \vfill
  \end{enumerate}
  \newpage


\item Let $f(x)=x-\ln(x)$ for $0.1\leq x\leq 2$. Find the value(s) of
  $x$ for which:
  \begin{enumerate}
  \item $f(x)$ has a critical point. Indicate which
    ones are maxima and which are minima.

    \vfill
    
  \item $f(x)$ has a global maximum or global minimum.

    \vfill
  \end{enumerate}
  \newpage
  
\item State the Mean Value Theorem.


\end{enumerate}

\end{document}
