\documentclass[11pt]{article} 
\usepackage{calc, tikz}
\usepackage[margin={1in,1in}]{geometry} 
\usepackage[hwkhandout]{hwk}
\usepackage[pdftitle={Calc 1
  Notes},colorlinks=true,urlcolor=blue]{hyperref}

\renewcommand{\theclass}{\textsc{math}1300: calculus I}
\renewcommand{\theauthor}{Tyson Gern}
\renewcommand{\theassignment}{Marginal Analysis}
\renewcommand{\dateinfo}{section 4.5}

\newcommand{\ds}{\displaystyle}

\begin{document}
\drawtitle

\begin{enumerate}
\item A company estimates that the total revenue, $R$, in dollars,
  received from the sale of $q$ items is
  \[
  R = \ln(1 + 1000q^2).
  \]
  Calculate and interpret the marginal revenue if $q = 10$.

  \vfill

\item The graph below shows cost and revenue. Illustrate the following
  quantities on the graph.
  \begin{enumerate}
  \item Fixed cost.
  \item The quantity that maximizes profit.
  \item The maximum profit.
  \end{enumerate}
  \begin{center}
    \begin{tikzpicture}[xscale = 4/5, yscale = 16/25]
      \draw[->] (0,0) -- (9,0);
      \draw[->] (0,0) -- (0,11);
      
      \draw[thick, domain=0:6.6, ->] plot[samples=200]
      function{.1*((x-3)**3+(x-3)) + 5} node[above] {$C$};

      \draw[thick, domain=0:8, ->] plot[samples=200]
      function{4*log(x+1)} node[below] {$R$};
    \end{tikzpicture}

  \end{center}

  \newpage

\item The revenue from selling $q$ items is $R(q) = 500q - q^2$, and
  the total cost is $C(q) = 10000 + 3q^2$.
  \begin{enumerate}
  \item At what quantity is profit maximized?

    \vfill
    
  \item What is the total profit at this production level?

    \vfill
    
  \end{enumerate}
  
  \newpage

\item The table below shows cost, $C(q)$ and revenue, $R(q)$.
  \begin{center}
    \begin{tabular}{l|rrrrrrr}
      $q$ & 0 & 500 & 1000 & 1500 & 2000 & 2500 & 3000\\ \hline
      $R(q)$ & 0 & 1500 & 3000 & 4500 & 6000 & 7500 & 9000\\
      $C(q)$ & 3000 & 3800 & 4200 & 4500 & 4800 & 5500 & 7400
    \end{tabular}
  \end{center}
  \begin{enumerate}
  \item At approximately what production level, $q$, is profit
    maximized?

    \vfill

  \item What is the price of the product?

    \vfill

  \item What are the fixed costs?

    \vfill
    
  \end{enumerate}

\item If $C'(500) = 75$ and $R'(500) = 100$, should the quantity
  produced be increased or decreased from $q = 500$ in order to
  increase profits?

  \vfill\vfill

  \newpage

\item The total cost of producing $q$ goods is given by:
  \[
  C(q) = 0.01q^3 - 0.6q^2 + 13q.
  \]
  \begin{enumerate}
  \item What is the fixed cost?

    \vfill

  \item What is the maximum profit if each item is sold for \$7?

    \vfill

  \item Suppose exactly 34 goods are produced. They all sell when the
    price is \$7 each, but for each \$1 increase in price, 2 fewer
    goods are sold. Should the price be raised, and if so by how much?

    \vfill
    
  \end{enumerate}

\end{enumerate}

\end{document}
