\documentclass[11pt]{article} 
\usepackage{calc}
\usepackage[margin={1in,1in}]{geometry} 
\usepackage[hwkhandout]{hwk}
\usepackage[pdftitle={Calc 1
  Notes},colorlinks=true,urlcolor=blue]{hyperref}

\renewcommand{\theclass}{\textsc{math}1300: calculus I}
\renewcommand{\theauthor}{Tyson Gern}
\renewcommand{\theassignment}{Global Extrema}
\renewcommand{\dateinfo}{section 4.2}

\newcommand{\ds}{\displaystyle}

\begin{document}
\drawtitle
\begin{enumerate}
\item Find all global extrema, if they exist, for the following
  functions on the given intervals.
  \begin{enumerate}
  \item $f(x)=3x^{1/3}-x$ on $[-1,8]$
  
    \vfill
  
  \item $g(x)=xe^{-x}$ on $(0,\infty)$

    \vfill
    
    \newpage

  \item $h(x)=\dfrac{1}{x^2}$ on $(0,\infty)$
    \vfill

  \item $P(x)=\dfrac{x^2}{x^2+1}+2$ on the whole real line
    \vfill 
    \newpage

  \item $\displaystyle Q(x)=e^{\left(e^x\right)}$ on $[-4,7]$
    \vfill

  \item $R(x)=3$ on $(1,4]$.
    \vfill 
  \end{enumerate}

\newpage


\item A grapefruit is straight up with an initial velocity of 50
  ft/sec.  The grapefruit is 5 feet above the ground when it is
  released.  It's height at time $t$ is given by
  \[
  y=-16t^2+50t+5.
  \]
  \begin{enumerate}
  \item What is the grapefruits maximum height? minimum height?
    
    \vfill
    
  \item What is the grapefruits maximum velocity? minimum velocity?
    
    \vfill
    
  \item What is the grapefruits maximum speed? minimum speed?
    
    \vfill
    
  \end{enumerate}

  \newpage
  
\item When an electric current passes through two resistors with
  resistance $r_1$ and $r_2$, connected in parallel, the combined
  resistance, $R$, can be calculated from the equation
  \[
  \frac{1}{R}=\frac{1}{r_1}+\frac{1}{r_2},
  \]
  Where $R$, $r_1$, and $r_2$ are positive.  Assume $r_2$ is constant.
  \begin{enumerate}
  \item Show that $R$ is an increasing function of $r_1$.
    \vfill
  \item Assume that $a$ and $b$ are positive numbers.  Where on the interval
    $[a,b]$ does $R$ take its maximum value?
    \vfill
  \end{enumerate}

  \newpage

\item Let $f(x)=ax^2+bx+c$, where $a$, $b$, and $c$ are constants.

  \begin{enumerate}
  \item Find the $x$-value of the critical point of $f(x)$.

    \vfill

  \item Under what conditions on $a$, $b$, and $c$ is the critical
    value a minimum? a maximum?

    \vfill
  \end{enumerate}


\end{enumerate}
\end{document}
